WASP-4 is accelerating towards the Earth

### 2020-01-20 paper/ms.tex
minor
better words

>>>>

\subsection{Constraints on companion masses and semi-major axes}

Given a linear radial velocity trend, we can place limits on the mass
and semi-major axis of any planetary or stellar companions in the
system.
The constraints on the two parameters are degenerate: $\dot{\gamma}
\propto M_{\rm p} a^{-2}$.
Nonetheless, the additional information from the Zorro images can help
limit the available parameter space by setting an outer limit on the
semimajor axis, and a maximum brightness (and thereby mass) of any
putative companions.

The general procedure we use to derive these constraints has been developed by
\citet{wright_linear_trends_2007}, \citet{montet_trends_2014},
\citet{knutson_friends_2014}, \citet{bryan_statistics_2016,bryan_excess_2019},
and others.
For this study, we closely follow the procedure of \citet{bryan_excess_2019}.

We begin by defining a $50\times50$ grid in true planetary mass and semimajor
axis, evenly spaced from 1 to 300$\,$$M_{\rm Jup}$ and 3 to 500$\,$${\rm AU}$.

We then consider the possibility that an additional companion in any particular
cell can explain the observed linear trend.

In each cell, we consider 500 hypothetical companions.

We assign each companion a mass and semimajor axis from log-uniform
distributions within the grid cell. We draw the inclination from a uniform
distribution in $\cos i$.  The eccentricity is drawn from
\citet{kipping_beta_2013}'s long-period exoplanet Beta distribution ($a=1.12$,
$b=3.09$).

For each simulated companion, we then draw a sample from the converged chains
of our initial model of WASP-4b, plus its linear trend. We subtract
the planet's orbital solution, leaving the linear trend.

Given $(a_{\rm c}, M_{\rm c}, e_{\rm c}$ for each simulated outer companion,
and the fixed instrument offsets and jitters from the MCMC chains, we then
perform a maximum likelihood fit for the time and argument of periastron of the
outer simulated companion.

We then convert the resulting $50\times50\times500$ cube of best-fit
log-likelihood values to probabilities, and average over the samples in
each grid cell to derive a probability distribution in mass and semi-major
axis.

The distribution is shown in {\bf Figure~X}.
